fig6

### 2020-02-18 analysis/22_symphony.Rmd
save files

```{r}

d4 %>% 
  filter(gene %in% c("PRL", "PRLR", "ESR2")) %>%
ggplot( aes(x = treatment, y = m, color = gene)) +
    geom_smooth(aes(x = as.numeric(treatment)), se = F) +
    facet_grid(gene~tissue, scales = "free")

>>>>

```{r}
d4 %>% 
  filter(gene %in% c("PRL", "PRLR", "ESR2")) %>%
ggplot( aes(x = treatment, y = m, color = gene)) +
    geom_smooth(aes(x = as.numeric(treatment)), se = F) +
    facet_grid(gene~tissue, scales = "free")

### 2020-02-18 analysis/figure-6.Rmd
save files

# Figure 4

@@

vsd_path <- "../results/DEseq2/manip/"   # path to the data
vsd_files <- dir(vsd_path, pattern = "*vsd.csv") # get file names
vsd_pathfiles <- paste0(vsd_path, vsd_files)
vsd_files

allvsd <- vsd_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name")  %>% 
  dplyr::rename("gene" = "X1")  %>% 
  pivot_longer(cols = blk.s031.pu.d_female_gonad_prolong:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "samples", values_to = "counts")

hypreplace <- read_csv("../results/DEseq2/manip/female_hypothalamus_hatch_extend_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 1) %>% pull(gene)
hypreplace

hypremove <- read_csv("../results/DEseq2/manip/female_hypothalamus_m.n2_hatch_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 1) %>% pull(gene)
hypremove

pitreplace <- read_csv("../results/DEseq2/manip/female_pituitary_hatch_extend_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 1) %>% pull(gene)
pitreplace

pitremove <- read_csv("../results/DEseq2/manip/female_pituitary_m.n2_hatch_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 1) %>% pull(gene)
pitremove

gonreplace <- read_csv("../results/DEseq2/manip/female_gonad_inc.d17_prolong_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 1) %>% pull(gene)
gonreplace

gonremove <- read_csv("../results/DEseq2/manip/female_gonad_inc.d17_m.inc.d17_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 1) %>% pull(gene)
gonremove

plottopgenes <- function(whichgenes, whichtissue, whichsex, mysubtitle, whichtstages){
  candidates  <- allvsd %>%
    filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
    dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/manip/'), "[", 2)) %>%
    dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
    dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
    dplyr::select(sex, tissue, treatment, gene, samples, counts) %>%
    filter(tissue == whichtissue, sex %in% whichsex)

  candidates$treatment <- factor(candidates$treatment, levels = alllevels2)

  p <- candidates %>%
    filter(treatment %in% whichtstages) %>%
    ggplot(aes(x = treatment, y = counts, fill = treatment, color = sex)) +
    geom_boxplot() + facet_wrap(~gene, scales = "free_y") + 
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme(axis.text.x = element_blank(),
          legend.position = "none",
          axis.title.x = element_blank(),
          strip.text = element_text(face = "italic")) +
    labs(y = mysubtitle) 
  return(p)

}

a <- plottopgenes(hypreplace, "hypothalamus", c("female"), "hypothalamus", c("hatch", "extend")) 
b <- plottopgenes(pitreplace, "pituitary", c("female"), "pituitary", c("hatch", "extend")) 
c <- plottopgenes(gonreplace, "gonad", c("female"), "gonads", c("inc.d17", "prolong"))

fig6a <- plot_grid(a,b,c, ncol = 1)

d <- plottopgenes(hypreplace, "hypothalamus", c("female", "male"), NULL, alllevels2) 
e <- plottopgenes(pitreplace, "pituitary", c("female", "male"), NULL, alllevels2) 
f <- plottopgenes(gonreplace, "gonad", c("female", "male"), NULL, alllevels2) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

fig6b <- plot_grid(d,e,f, ncol = 1)

fig6 <- plot_grid(fig6a, fig6b, rel_widths = c(1,2))
fig6
```

>>>>

# Figure 6

@@

DEGchar <- read_csv("../results/DEGs-char.csv")
DEGmanip <- read_csv("../results/DEGs-manip.csv")
DEGall <- rbind(DEGchar, DEGmanip)
tail(DEGall)

hatchnocontrol <- DEGall %>% filter(grepl("inc.d17", comparison)) %>% filter(!grepl("control", comparison))
hatchnocontrol %>% group_by(comparison) %>% summarize(n = n())

incd17hatch <- DEGall %>% filter(comparison == "inc.d17_hatch") %>%
  arrange(gene) %>% distinct(comparison, gene)
incd17hatch

incd17prolong <- DEGall %>% filter(comparison == "inc.d17_prolong") %>%
  arrange(gene) %>% distinct(comparison, gene)
incd17prolong

bothincs <- full_join(incd17hatch,incd17prolong, by = "gene" )
bothincs

onlyhatch <- subset(bothincs, is.na(bothincs$comparison.y))
onlyhatch
```
